Solar jet observed at the limb in SDO/SST

### 2016-04-22 paper/ms_temp_paper.tex
Start the doppler section

>>>>

Possibly the most valuable information to be gained with respect to jets is pertaining to it rotational behaviour, therefore, we will use the spectral increments from the CRISP instrument to obtain line of sight Doppler velocities.
There is however a hindrance with this, there are two seperate forms of the emmission spectra within the image.
The region where the jet initialises, is on disk, and as a result the spectral analysis reveals an absorption spectra.
Over the limb, however, the spectral profile changes to emission and we find two peaks.
As a consequence of this, finding the total shift away from the core, $6562.8$ nm is made more complex.
For pixel points which are on-disk, we fit a single Gaussian and calculate the mean, as is standard, and for the two peak spectra, we have utilised a double Gaussian.
However the problem becomes when we need to change between the two routines.

As a solution to this problem we have utilised a Markov Chain Monte Carlo (MCMC) method to find the most accurate fit and the Bayesian Information Criterion (BIC) to test which of the two fits is most appropriate from a given line.
